The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-08 paper/sections/results.tex
beam stuff updated

We demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
\revise{We further perform a basic \emph{quantitative} comparison against FEM by measuring the maximum deflection of the beam as we increase the number of patches along the beam. In \reffig{plot_beam_deflection}, the maximum beam deflection of the SEM beams is reported as a percentage of the FEM beam's maximum deflection. The parameters of the experiment match that of the previous qualitative test.}

@@

We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of \revise{22} independent NURBS patches, shows good agreement with FEM. Each subdivision of the NURBS beam enables more complicated kinematics, 
but very few surface elements are needed to produce compelling results.

@@

\revise{Additionally, we perform a twisting beam experiment on the 22 part beam model. Despite the relatively small number of NURBS patches, we see in \reffig{beam_twist} that the quadratic polynonmials permit complex deformation.}

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/beam_twist.pdf}
  \caption{\revise{With the left end of the beam held fixed, we show the result of rotating the right end of the 22 part beam up to 360 degrees.}}
  \label{fig:beam_twist}
\end{figure}

>>>>

We demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
\revise{We further perform a basic \emph{quantitative} comparison against FEM by measuring the deflection of the beam at resting position as we increase the number of patches along the beam. In \reffig{plot_beam_deflection}, the beam deflection of the SEM beams is reported as a percentage of the FEM beam's deflection.}

@@

We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of \revise{26} independent NURBS patches, shows good agreement with FEM. Each subdivision of the NURBS beam enables more complicated kinematics, 
but very few surface elements are needed to produce compelling results.

@@

\revise{Additionally, we perform a twisting beam experiment on a 22 part beam model. Despite the relatively small number of NURBS patches, we see in \reffig{beam_twist} that the quadratic polynonmials permit complex deformation.}

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/beam_twist.pdf}
  \caption{\revise{With the left end of the beam held fixed, we show the result of rotating the right end of a 22 part beam up to 360 degrees.}}
  \label{fig:beam_twist}
\end{figure}
